03_wrangle

### 2020-08-27 analysis/03_datawrangling.Rmd
now with sequential comparisons

allvsd <- vsd_pathfiles %>%
  setNames(nm = .) %>% 
  map_df(~read_csv(.x), .id = "file_name")  %>% 
  dplyr::rename("gene" = "X1") %>% 
  pivot_longer(cols = L.G118_female_gonad_control:y98.o50.x_male_pituitary_inc.d3, 
               names_to = "samples", values_to = "counts") 
allvsd %>% select(-file_name) %>% head()

@@

# sequential in 2 or more comparisons
wideDEGsSequential <- wideDEGscandidates %>%
  select(sextissue,gene, "control_bldg", "bldg_lay", "lay_inc.d3", "inc.d3_inc.d9",
         "inc.d9_inc.d17", "inc.d17_hatch", "hatch_n5", "n5_n9") %>%
  mutate(totalNA = rowSums(is.na(.))) %>%
  filter(totalNA < 8) %>%
  arrange(totalNA, gene, sextissue) %>%
  #arrange( gene, sextissue) %>%
  select(-totalNA) %>% 
  replace(., is.na(.), "")
wideDEGsSequential

@@

filteredDEGs <- allDEG %>%
  filter(lfc > 1.1 | lfc < -1.1 )
dim(allDEG)
dim(filteredDEGs)

@@

filteredDEGs <- allDEG %>%
  filter(lfc > 1.1 | lfc < -1.1 ) %>%
  filter(tissue == "pituitary")

@@

venn.diagram(
  x = list(inc.d3_m.inc.d3DEGs,hatch_m.n2DEGs,
            inc.d9_m.inc.d9DEGs, inc.d17_m.inc.d17DEGs),
  category.names = c("Inc 3" , "Hatch" , "Inc 9", " Inc 17"),
  filename = '../figures/venn-pit.png',
  output=FALSE,
  print.mode = "raw",
  imagetype = "png",
  col=c("#CDCDCD", '#262625', '#959595','#959595'),
  fill = c("#CDCDCD", "#262625", "#959595", "#959595"),
  main = "Pituitary - Offspring Removal",
  sub = "Differentially expressed genes relative to internal controls"
  )

@@

filteredDEGs <- allDEG %>%
  filter(lfc > 1.1 | lfc < -1.1 ) %>%
  filter(tissue == "pituitary")

>>>>

allvsd <- vsd_pathfiles %>%
  setNames(nm = .) %>% 
  map_df(~read_csv(.x), .id = "file_name")  %>% 
  dplyr::rename("gene" = "X1") %>% 
  #pivot_longer(cols = L.G118_female_gonad_control:y98.o50.x_male_pituitary_inc.d3, 
               #names_to = "samples", values_to = "counts") 
  pivot_longer(cols = L.G118_female_hypothalamus_control.NYNO:y98.g54_female_hypothalamus_m.hatch, 
               names_to = "samples", values_to = "counts") 
allvsd %>% select(-file_name) %>% head()

tail((allvsd))
```

@@

# sequential in 2 or more comparisons
wideDEGsSequential <- wideDEGscandidates %>%
  select(sextissue,gene, "control_bldg", "bldg_lay" #, 
         #"lay_inc.d3", "inc.d3_inc.d9",
         #"inc.d9_inc.d17", "inc.d17_hatch", "hatch_n5", "n5_n9"
         ) %>%
  mutate(totalNA = rowSums(is.na(.))) %>%
  filter(totalNA < 8) %>%
  arrange(totalNA, gene, sextissue) %>%
  arrange( gene, sextissue) %>%
  select(-totalNA) %>% 
  replace(., is.na(.), "NS")
wideDEGsSequential

@@

filteredDEGs <- allDEG %>%
  filter(lfc > 0.14 | lfc < -0.14 )
dim(allDEG)
dim(filteredDEGs)

@@

filteredDEGs <- allDEG %>%
  filter(lfc > 0.14 | lfc < -0.14 ) %>%
  filter(tissue == "hypothalamus")

@@

venn.diagram(
  x = list(inc.d3_m.inc.d3DEGs,hatch_m.n2DEGs,
            inc.d9_m.inc.d9DEGs, inc.d17_m.inc.d17DEGs),
  category.names = c("Inc 3" , "Hatch" , "Inc 9", " Inc 17"),
  filename = '../figures/venn-hyp.png',
  output=FALSE,
  print.mode = "raw",
  imagetype = "png",
  col=c("#CDCDCD", '#262625', '#959595','#959595'),
  fill = c("#CDCDCD", "#262625", "#959595", "#959595"),
  main = "Hypothalamus - Offspring Removal",
  sub = "Differentially expressed genes relative to internal controls"
  )

@@

filteredDEGs <- allDEG %>%
  filter(lfc > 1.1 | lfc < -1.1 ) %>%
  filter(tissue == "hypothalamus")
